The reference model approach in feature selection problems \vspace{.1in}

### 2019-07-16 paper/ref_approach.tex
edit section 2

The main assumption under any reference model approach is that we
operate in a $\mathcal{M}$-\textit{complete} framework
\citep{book:bernardo_smith,vehtari2012survey}, that is we have constructed a
model which reflects in the best way our beliefs about the future
data. In practice, this would often be the full-encompassing model
(including as submodels all models we consider having non-zero prior
probability) which has passed model checking and criticism \citep[see,
e.g.][]{gelman2013bayesian}.

A good predictive model is able to filter part of the noise present in the data. The noise is the main source of the instability and tends to obscure the relevance of the covariates in relation to the target variable of interest. Indeed, let us consider the following explanatory example taken from \cite{paper:projpred}. The data generation mechanism is
\begin{alignat}{2} \label{eq:simulated_data}
     &f\sim N(0,1) && \nonumber \\ 
     Y|&f\sim N(f,1) && \\
     X_{j}|&f \overset{iid}{\sim} N(\sqrt{\rho}f,1-\rho) \quad &&j=1,..,k \nonumber \\
     X_{j}|&f \overset{iid}{\sim} N(0,1) &&j=k+1,..,p \nonumber,
\end{alignat}
where $f$ is the latent variable of interest of which $Y$ is a noisy observation. The first $k$ covariates are strongly related to the target variable $Y$ and correlated among themselves. Precisely, $\rho$ is the correlation among any pair of the first $k$ covariates, whereas $\sqrt{\rho}$ and $\sqrt{\rho/2}$ are the level of correlation between any relevant covariate and respectively $f$ and $Y$. If we had an infinite amount of observations, the sample correlation would be equal to the true correlation, though, even in this ideal asymptotic regime, the correlation computed would be still a biased indicator of the true relevance of each variable with respect to the latent variable of interest due to the intrinsic noisy nature of $Y$.

When using a reference model, we first model $f$ using all the covariates $\{X_{j}\}_{j=1}^{p}$ taking into account that we observe noisy $Y$. If our model is good, we are able to describe $f$ better than the noisy $Y$, which improves the accuracy in the estimation of the relevance of the covariates.  Figure \ref{fig:correlation} shows the scatter plot of the absolute value of the sample correlation of each feature with the point predictions $\{\hat{y}\}_{i=1}^{n}$ of a reference model, in this case posterior predictive means of model \eqref{eq:ref_mod}, against the absolute value of the sample correlation of each feature with the noisy observations $\{y\}_{i=1}^{n}$. Looking at the marginal distributions, we can see that using a reference model to filter out noise in the data the two groups of features (relevant and non-relevant) can be better distinguished than when the correlation is computed using directly the observed noisy data.

@@

% In Figure \ref{fig:correlation} the reference model filters the noise.
% This simple idea is what happens every time a reference model is used, as it is evident for example in the preconditioning by \cite{paul2008preconditioning} or in the draw-by-draw projection for GLMs by \cite{paper:original_proj}.\\
% Above the correlation was used to estimate the relevance of a covariate.  
As an another example, let us consider a candidate submodel in a feature selection process and let us refer with $\pi$ to the parameter distribution of the submodel and with $q_{\pi}(\tilde{y})$ to the induced predictive distribution. We would like to choose $\pi$ in order that the latter maximises some predictive performance utility, as the expected log-predictive density (elpd) defined as:
\
\begin{equation}\label{eq:elpd}
\text{elpd}[q_{\pi}]=\int \text{log}\,q_{\pi}(\tilde{y})p_{t}(\tilde{y})d\tilde{y} 
\end{equation}
If we refer to the posterior predictive distribution of a reference model with $p(\tilde{y}|D)$, where $D$ stands for the data on which we condition on, we can approximate \eqref{eq:elpd} using $p(\tilde{y}|D)$ instead of the true, unknown, data generation mechanism $p_{t}(\tilde{y})$. The maximisation of the elpd using the reference model predictive distribution is equivalent to the minimisation of the KL divergence between the reference model predictive distribution and the submodel one:
\
\begin{equation} \label{proj_as_filter}
\underset{\pi}{\text{max}} \; \int \text{log}\,q_{\pi}(\tilde{y})p(\tilde{y}|D)d\tilde{y} \leftrightarrow \underset{\pi}{\text{min}} \; \text{KL}[p(\tilde{y}|D)||q_{\pi}(\tilde{y})] 
\end{equation}
The term on the right-hand side of Equation \eqref{proj_as_filter} describes what is referred as the projection of the predictive distribution, which is the general idea behind the projection predictive approach. Again the reference model is acting as a filter, or substitute, on data.

@@

Relying on the idea of the reference model as a noise-filter, a simple reference model approach, which can be used on top of any feature selection procedure, consists in substituting the target observations with a point prediction of the reference model, e.g. the posterior predictive mean. Afterwards, any method for feature selection can be used. Note that we do not argue that such reference model approach should be used as a feature selection tool in real applications; there are many other and more sophisticated ones available in the literature. The reason of this simple approach is to have a fair comparison between using a reference model or not with exactly the same selection procedure. Other kinds of comparison, as the one in Section \ref{projection}, work well as motivational examples, but fail in terms of generality, resulting in a not principled comparison since the presence of the reference model is not the only thing differentiating the two procedures. In Section \ref{comparison} we compare some well-known methods from the literature using both such reference model approach and the original data, observing at the end of the selection higher stability and quality of the selection thanks to the reference model.

@@

As a motivational example to the study of the consequences of the use of a reference model in feature selection problems, we show its application in the form of the projection predictive approach, which uses the reference model to project the posterior samples in the submodels. The \texttt{R}-package \texttt{projpred} (available at \url{https://CRAN.R-project.org/package=projpred}) implements the projection in case of submodels in the family of the generalised linear models and, additionally, it provides a framework to choose the optimal submodel size through a predictive utility comparison between the submodels and the reference model. 
\\
We now summarise the workflow of the projection predictive approach in the particular case of the draw-by-draw projection \cite[original formulation by][]{paper:original_proj}, following \cite{paper:projpred}. Assume to have $n$ statistical units with target values $\{y_{i}\}_{i=1}^{n}$ and a set of observed covariates, the main steps are the following:
\begin{enumerate}
\item Devise and fit a reference model. Let $\{\boldsymbol{\theta}_{*}^{s}\}_{s=1}^{S}$ be the set of S posterior samples of the vector parameter of the model.
\item Rank the covariates using a heuristics and consider as candidate submodels the nested ones, starting to include the best ranked feature. The submodel are naturally identified by their model size.
\item For each submodel, project the reference model samples as follows:
\begin{equation}\label{eq:draw_by_draw}
\boldsymbol{\theta}_{\perp}^{s} = \underset{\boldsymbol{\theta^{s}}\in\Theta}{\text{argmin}} \frac{1}{n}\sum_{i=1}^{n}\text{KL}\;[p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})\,||\,q(\tilde{y}_{i}|\boldsymbol{\theta}^{s})] \quad s=1,..,S
\end{equation}
where $p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})$ stands for the model distribution of the reference model with parameters fixed at the sample value $\boldsymbol{\theta}_{*}^{s}$ and conditioning on all the covariates related to the statistical unit (identified by the subscript $i$ in the variable $\tilde{y}_{i}$), whereas $q(\tilde{y}_{i}|\boldsymbol{\theta}^{s})$ the same but for the submodel. The projected samples correspond to the submodel parameter distribution.
\item For each submodel (size), test the predictive performance.
\item Choose the smallest submodel (size) that is sufficiently close to the reference model prediction utility score.
\end{enumerate}

Expression \eqref{eq:draw_by_draw} is not an easy optimisation problem, but in the special case of submodels in the GLMs family, \eqref{eq:draw_by_draw} reduces to a maximum likelihood estimation problem, which can be easily optimised (e.g. using iteratively reweighted least squares alogirthm, IRLS). For further details on \texttt{projpred} workflow and implementation see \cite{paper:projpred}.

We show the benefits of the reference model in the form of the projection approach (projpred) with respect to the stepwise backward regression (steplm) using the body fat data \citep{johnson1996fitting}. The analysis is based on Vehtari's \texttt{R}-notebook available at \url{https://avehtari.github.io/modelselection/bodyfat.html}, which is inspired by \cite{paper:bodyfat}. The target variable of interest is the amount of body fat, which is measured with a complex and expensive procedure, and the original covariates are 13 anthropometric measurements (e.g. height, weight), some of which are highly correlated among themselves and thus provide some challenges in the model selection, for a total of 251 observations. The goal is to find the simplest model which is able to describe, that is to predict, sufficiently well the amount of fat. We use the same data again later in Section \ref{real-world-data}.

\cite{paper:bodyfat} report results using the stepwise backward elimination with a significance level of 0.157 with AIC selection, fixing abdomen and height to be always included in the model. We implement the stepwise backward elimination via AIC without fixing any variable, and the selection via projection: the reference model includes all the covariates using as a prior the regularised horseshoe, submodels are explored using a forward search and the predictive utility is the expected log-predictive density (elpd) estimated using PSIS-LOO \citep{paper:psis_loo}. The experiments are implemented in \texttt{R}: the stepwise elimination is carried out combining the \texttt{step} and \texttt{lm} functions, whereas the selection via projection using the \texttt{projpred} package. In order to automatise the latter, we select the submodel size as the smallest one which has an elpd score higher than the reference model score with probability 0.05. The inclusion frequencies of each feature in the final model after 100 bootstrap samples are depicted in Figure \ref{fig:inclusion_frequencies}: the projection predictive approach has only two variables with inclusion frequencies above 50\% (abdomen is the only included always), the third most included is `wrist' at 44\% and the fourth is `height' at 35\%, while the stepwise regression has seven features above 50\%. Such a lower stability of the stepwise regression can be observed also in the bootstrap model selection frequencies reported in Table \ref{tab:model_frequencies}. The first five selected models have a cumulative frequency of 76\% with projpred, whereas with the stepwise regression only of 14\%. In addition to that we note that the size of the selected model is much smaller when using projpred.

@@

Table \ref{tab:model_performances} reports the predictive performances, in terms of root mean square error, of the full model and the correspondent selected model using both the projection predictive approach and the stepwise backward elimination. We also repeat the selection after adding uncorrelated noisy features up to a total of 100 covariates and report in such a case both the size of the selected model and the number of selected noisy features. Whilst with the original data we do not observe any gain using projpred in terms of predictive performance (we do observe a smaller size for the selected model, however with a much higher computational cost), when noisy features are added the projection is able to notably improve the predictive performance keeping the same submodel size, whereas the stepwise regression selects a much larger submodel including a large number (13 over 19) of noisy features.

\begin{table}[tp]
\scriptsize
\centering
\begin{tabular}{l|r|r|r|r}
  \hline
 & rmse.full & rmse.sel & size.sel & noisy.sel \\ 
  \hline
projpred & 4.35 & 4.47 & 2 & -  \\
steplm & 4.38 & 4.47 & 7 & - \\
\hline
\hline
projpred & 4.58 & 4.54 & 2 & 0  \\
steplm & 5.89 & 5.43 & 19 & 13 \\
   \hline
\end{tabular}
\caption{Model predictive performances with original data (first two rows) and adding noisy features (last two rows) estimated with 10-fold cross-validation.}
\label{tab:model_performances}
\end{table}

@@

We can consider the reference model approach as a family of methods, thus providing an answer to the question what the computational burden is, is not possible, because not unique. It is possible to identify a common and inevitable overhead though, that is the cost of fitting the reference model. In the simple reference model approach we have described at the end of Section \ref{reference-model-approach}, it is actually the only added cost. In general, a full Bayesian model is advisable in order to have the best predictive performance, however including all the available features can be often quite computationally demanding. In such a case a first possible speed-up could be using screening or dimensionality reduction techniques, as for example the supervised principal components \citep{bair2006prediction,piironen2018}. However, in some cases this does not always result in an appreciable speed-up, as when there are several predictive and not correlated features and, thus, many of them have to be included in the reference model anyway. Other alternatives could be fixing some parameters with their maximum marginal likelihood value (typically referred as empirical Bayes) or use a frequentist approach, if predictions are good enough.

The comparison example between projpred and steplm shows that such additional computational burden can be worth it. In the case of the projection predictive approach it results in sparser submodels, which can result in saving time and general costs using the selected model for future predictions. Table \ref{tab:model_performances} shows that there could be even an improvement in the prediction ability, thus justifying more additional computational costs in the selection. More benefits obtainable through the reference model are provided in the experiments of Section \ref{comparison}.

>>>>

The main assumption under any reference model approach is that we
operate in an $\mathcal{M}$-\textit{complete} framework
\citep{book:bernardo_smith,vehtari2012survey}. That is, we assume to be able to construct a model whose predictions reflect the best available description of the uncertainty of future data. In practice, this will often be the full-encompassing model
(including all models we consider having non-zero prior
probability as submodels) which has passed model checking and criticism \citep[see,
e.g.][]{gelman2013bayesian}.

A good predictive model is able to filter parts of the noise present in the data. The noise is the main source of the instability and tends to obscure the relevance of the covariates in relation to the target variable of interest. Indeed, let us consider the following explanatory example taken from \cite{paper:projpred}. The data generation mechanism is
\begin{alignat}{2} \label{eq:simulated_data}
     &f\sim N(0,1) && \nonumber \\ 
     Y|&f\sim N(f,1) && \\
     X_{j}|&f \overset{iid}{\sim} N(\sqrt{\rho}f,1-\rho) \quad &&j=1,..,k \nonumber \\
     X_{j}|&f \overset{iid}{\sim} N(0,1) &&j=k+1,..,p \nonumber,
\end{alignat}
where $f$ is the latent variable of interest of which $Y$ is a noisy observation. The first $k$ covariates are strongly related to the target variable $Y$ and correlated among themselves. Precisely, $\rho$ is the correlation among any pair of the first $k$ covariates, whereas $\sqrt{\rho}$ and $\sqrt{\rho/2}$ are the level of correlation between any relevant covariate and, respectively, $f$ and $Y$. If we had an infinite amount of observations, the sample correlation would be equal to the true correlation between $X_j$ and $Y$. However, even in this ideal asymptotic regime, this  correlation would still remain a biased indicator of the true relevance of each covariate (represented by the correlation between $X_j$ and $f$) due to the intrinsic noisy nature of $Y$.

When using a reference model, we first obtain predictions for $f$ using all the covariates $\{X_{j}\}_{j=1}^{p}$ taking into account that we have only observed the noisy representation $Y$ of $f$. If our model is good, we are able to describe $f$ better than $Y$ itself can, which improves the accuracy in the estimation of the relevance of the covariates.  Figure \ref{fig:correlation} illustrates this process in the form of a scatter plot of (absolute) correlations of the covariates with $Y$ against the corresponding correlations with the predictions of a reference model (in this case the posterior predictive means of model \eqref{eq:ref_mod}; see Section \ref{simulated-data}). Looking at the marginal distributions, we see that using a reference model to filter out noise in the data, the two groups of features (relevant and non-relevant) can be distinguished much better than when the correlation is computed using the observed noisy data directly.

@@

% In Figure \ref{fig:correlation} the reference model filters the noise.
% This simple idea is what happens every time a reference model is used, as it is evident for example in the preconditioning by \cite{paul2008preconditioning} or in the draw-by-draw projection for GLMs by \cite{paper:original_proj}.\\
% Above the correlation was used to estimate the relevance of a covariate.  
As an another example, let us consider a candidate submodel in a feature selection process and let us refer to the parameter distribution of the submodel by $\pi$ and to the induced predictive distribution by $q_{\pi}(\tilde{y})$. We would like to choose $\pi$ so that $q_{\pi}(\tilde{y})$ maximises some predictive performance utility, for example, the expected log-predictive density (elpd) defined as:
\
\begin{equation}\label{eq:elpd}
\text{elpd}[q_{\pi}]=\int \text{log}\,q_{\pi}(\tilde{y})p_{t}(\tilde{y})d\tilde{y},
\end{equation}
where $p_{t}(\tilde{y})$ denotes the (usually unknown) true generating mechanism of future data $\tilde{y}$. If we refer to the posterior predictive distribution of a reference model with $p(\tilde{y}|D)$, where $D$ stands for the data on which we conditioned on, we can approximate \eqref{eq:elpd} using $p(\tilde{y}|D)$ instead of the true data generation mechanism $p_{t}(\tilde{y})$. The maximisation of the elpd using the reference model predictive distribution is equivalent to the minimisation of the KL divergence between the reference model's and the submodel's predictive distributions:
\
\begin{equation} \label{proj_as_filter}
\underset{\pi}{\text{max}} \; \int \text{log}\,q_{\pi}(\tilde{y})p(\tilde{y}|D)d\tilde{y} \leftrightarrow \underset{\pi}{\text{min}} \; \text{KL}[p(\tilde{y}|D)||q_{\pi}(\tilde{y})] 
\end{equation}
The term on the right-hand side of Equation \eqref{proj_as_filter} describes what is referred to as the projection of the predictive distribution, which is the general idea behind the projection predictive approach (cite). Again the reference model is acting as a filter, or substitute, on data.

@@

Relying on the idea of the reference model as a noise-filter, a generic reference model approach, which can be used on top of any feature selection procedure, consists of simply substituting the target observations with corresponding point predictions of the reference model, for instance, the posterior predictive means. Afterwards, any method for feature selection can be used. Note that we do not argue that such a reference model approach should necessarily be used as is for feature selection in real applications. There are several more sophisticated reference model approaches available in the literature (cite), which are likely to yield even better results. Rather, the reason for focussing on this simple version is to enable a fair comparison between a reference model and a purely data based approach when otherwise using the same selection procedures. Other kinds of comparisons, as the one presented in Section \ref{projection}, work well as motivational examples but fail in terms of generality since the presence or absence of a reference model is not the only aspect differentiating the two procedures. We will come back to the more general comparison in Section \ref{comparison}.

%we compare some well-known methods from the literature using both such reference model approach and the original data, observing at the end of the selection higher stability and quality of the selection thanks to the reference model.

@@

As a motivational example to the implications of using a reference model in feature selection problems, we show its application in the form of the projection predictive approach, which uses the reference model to project the posterior samples to the submodels (cite). The \texttt{R}-package \texttt{projpred} (available at \url{https://CRAN.R-project.org/package=projpred}) implements the projection in case of submodels in the family of the generalised linear models and, additionally, it provides a framework to choose the optimal submodel size through a predictive utility comparison between the submodels and the reference model. 
\\
We now summarise the workflow of the projection predictive approach in the particular case of the draw-by-draw projection \cite[original formulation by][]{paper:original_proj}, following \cite{paper:projpred}. Suppose we have observed $n$ statistical units with target values $\{y_{i}\}_{i=1}^{n}$ and a set of observed covariates for which we want to obtain a minimally relevant subset. Than, the main steps are the following:
\begin{enumerate}
\item Devise and fit a reference model. Let $\{\boldsymbol{\theta}_{*}^{s}\}_{s=1}^{S}$ be the set of $S$ posterior samples of the reference model's parameters.
\item Rank the covariates according to their relevance using some heuristics and consider as candidate submodels only those which preserve this order,  starting from including only the highest ranked covariate (the submodels are then naturally identified by their model size). This is not strictly necessary but reduces the number of submodels to consider in the following steps.
\item For each submodel, project the reference model's samples as follows:
\begin{equation}\label{eq:draw_by_draw}
\boldsymbol{\theta}_{\perp}^{s} = \underset{\boldsymbol{\theta^{s}}\in\Theta}{\text{argmin}} \frac{1}{n}\sum_{i=1}^{n}\text{KL} \left( p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})\;||\;q(\tilde{y}_{i}|\boldsymbol{\theta}^{s}) \right) \quad s=1,..,S
\end{equation}
where $p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})$ stands for the predictive distribution of the reference model with parameters fixed at the posterior sample $\boldsymbol{\theta}_{*}^{s}$ and conditioning on all the covariate values related to the statistical unit (identified by the subscript $i$), whereas $q(\tilde{y}_{i}|\boldsymbol{\theta}^{s})$ is the predictive distribution of the submodel. The projected samples $\boldsymbol{\theta}_{\perp}^{s}$ then correspond to the submodel's parameter distribution.
\item For each submodel (size), test the predictive performance for instance via cross-valdiation.
\item Choose the smallest submodel (size) that is sufficiently close to the reference model's predictive utility score.
\end{enumerate}

Expression \eqref{eq:draw_by_draw} is not an easy optimisation problem in general, but in the special case of submodels for the family of generalize lineder models, \eqref{eq:draw_by_draw} reduces to a maximum likelihood estimation problem, which can be easily optimised (cite). For further details on the projective prediction workflow and implementation see \cite{paper:projpred}.

We show the benefits of the reference model in the form of the projection approach (projpred) with respect to the stepwise backward regression (steplm) using the body fat data \citep{johnson1996fitting}. The analysis is based on Vehtari's \texttt{R}-notebook available at \url{https://avehtari.github.io/modelselection/bodyfat.html}, which is inspired by \cite{paper:bodyfat}. The target variable of interest is the amount of body fat, which is measured with a complex and expensive procedure. Additionally, we have information about 13 covariates which are anthropometric measurements (e.g., height and weight), some of which are highly correlated among themselves and thus provide some challenges in the model selection. In total, we have 251 observations. The goal is to find the simplest model which is able to predict the amount of fat sufficiently well. We use the same data again later on in Section \ref{real-world-data}.

\cite{paper:bodyfat} report results using steplm with a significance level of 0.157 with AIC selection, fixing abdomen and height to be always included in the model. Here, we implement steplm via AIC without fixing any variable. For selection via projpred, the reference model includes all the covariates, we regularize model complexity with a regularised horseshoe prior on the covariate coefficients (cite), submodels are explored using forward search, and the predictive utility is the expected log-predictive density (elpd) estimated using PSIS-LOO \citep{paper:psis_loo}. The experiments are implemented in \texttt{R} (cite). The steplm approach is carried out combining the \texttt{step} and \texttt{lm} functions, whereas the selection via projpred is done with the \texttt{projpred} package. In order to automatise the latter, we select the submodel as the one with the smallest size which has an elpd score higher than the reference model score with probability 0.05. The inclusion frequencies of each feature in the final model after 100 bootstrap samples are depicted in Figure \ref{fig:inclusion_frequencies}. The projpred approach has only two variables, 'abdomen' and 'weight', with inclusion frequencies above 50\% ('abdomen' is the only included always), the third most included is `wrist' at 44\%, and the fourth is `height' at 35\%, while steplm has seven features above 50\%. Such a lower stability of steplm can be observed also in the bootstrap model selection frequencies reported in Table \ref{tab:model_frequencies}. For exaple, the first five selected models have a cumulative frequency of 76\% with projpred, but only of 14\% with steplm. In addition, we note that the size of the selected model is much smaller when using projpred.

@@

Table \ref{tab:model_performances} reports the predictive performances, in terms of root mean square error, of the full model and the corresponding selected submodel using both projpred and steplm. We also repeat the selection after adding truely uncorrelated (i.e., irrelevant) features up to a total of 100 covariates. For this experiment, we report both the size of the selected submodel and the number of selected irrelevant features. Whilst, with the original data, we do not observe any gain using projpred in terms of predictive performance, what we do observe is a smaller size for the selected submodel, at the cost of a higher computation time compared to steplm. However, when additional irrelevant features are added, projpred is able to notably improve the predictive performance keeping the same submodel size, whereas steplm selects a much larger submodel also including a large number of irrelvant features (13 irrelevant out of a total of 19 selected features).

\begin{table}[tp]
\scriptsize
\centering
\begin{tabular}{l|r|r|r|r}
  \hline
 & RMSE(Full) & RMSE(Sel) & Size(Sel) & SizeIr(Sel) \\ 
  \hline
projpred & 4.35 & 4.47 & 2 & -  \\
steplm & 4.38 & 4.47 & 7 & - \\
\hline
\hline
projpred & 4.58 & 4.54 & 2 & 0  \\
steplm & 5.89 & 5.43 & 19 & 13 \\
   \hline
\end{tabular}
\caption{Model predictive performances with original data (first two rows) and adding noisy features (last two rows) estimated with 10-fold cross-validation. Abbreviations: Full = full model; Sel = selected submodel; Size = total number of included covariates; SizeIr = number of included irrelevant covariates.}
\label{tab:model_performances}
\end{table}

@@

We consider the reference model approach as a family of methods, thus providing a general answer to the question of computational burden is not possible because not unique. It is possible to identify a common and inevitable overhead, though, which is the cost of fitting the reference model. In the simple ''bare-bones'' reference model approach we have described above, it is actually the only added cost. In general, a full Bayesian model is advisable in order to have the best predictive performance. However, including all the available features can often be quite computationally demanding. In such a case, a first possible speed-up could be using screening or dimensionality reduction techniques, as for example the supervised principal components \citep{bair2006prediction,piironen2018}. However, in some cases, this does not always result in an appreciable speed-up. For example, when there are several predictive but mutually uncorrelated features, all of them  have to be included in the reference model anyway. Other alternatives could be fixing some parameters to their maximum marginal likelihood value (typically referred as empirical Bayes; cite) or use a completely frequentist approach, if predictions are good enough.

The comparison example between projpred and steplm shows that such additional computational burden can be worth it. We found that the reference model approach (projpred) selected much sparser submodels, which can result in saving time and general costs using the selected model for future predictions. Table \ref{tab:model_performances} displays that there could even be an improvement in the predictive ability compared to the full model, thus justifying more additional computational costs in the selection procedure. More benefits obtainable through a reference model approach are provided in the experiments discussed in the upcoming section.
